Prefetching SPARQL query cacher

### 2016-05-31 dissertation/related.tex
add todo
HERMES frist draft

\todo{\cite{adali1996query}}

@@

Recently, Papailiou et al. \cite{papailiou2015graph} made an extensive
study of SPARQL caching, addressing some of the same problems as the
present work, except for our emphasis on deployment on proxies in the
Internet and integration with HTTP-based caching.  \todo{reread the
  paper more here}

@@

>>>>

Two papers that span nearly two decades of research are of particular
interest: The HERMES system \cite{adali1996query} considered query
processing and cost-model based optimisation in a mediator system
where the mediator does not have access to source statistics
information. Recently, Papailiou et al. \cite{papailiou2015graph}
made an extensive study of SPARQL caching, addressing some of the same
problems as the present work.

Even though these do not share our perspective, which is deployment on
proxies in the Internet and integration with HTTP-based caching, these
contributions provide important context.

HERMES \cite{adali1996query} provided motivation for
\cite{sec:conpush}, but is also important prior art for the work in
Chapter~\ref{sec:tpfcacheplanning}. An important concept in the HERMES
system is ``invariants''. They are, in our terminology, patterns that
do not need to be looked up remotely, but can be integrated in the
query answer by the mediator. The expectation in HERMES is that such
invariants will be encoded by a domain expert. The Attean framework
provides facilities to do so by using traits. Attean can also pass the
task of computing a scalar cost metric by a similar mechanism, but
HERMES has a more advanced cost model in that it has a cost vector
with estimates for time required to find the first answer, time to
find all answers and the cardinality of the answer set. Caching
summary statistics is another important feature of HERMES, and it also
contributes lossy and lossless summaries, for the purpose of saving
space and reduce the time it takes to compute a cost estimate. HERMES
further has a query rewriter and optimiser, that rewrites the query
taking into account the cache and the invariants. While HERMES is more
general than what I detail in Chapter~\ref{sec:tpfcacheplanning}, we
note that while invariants could be coded in Attean, a SPARQL query
cache should be oblivious to domain knowledge and therefore shouldn't
assume any invariants, except in the possible but unlikely case where
the remote server declares that an infinite freshness lifetime for the
result of a certain graph pattern. While statistics summarisation is
relevant and should be studied in future work, we note that with a
Linked Data Fragments server, a cardinality estimate is required to be
available for every triple pattern, and is also cacheable with the
same constraints as the data themselves.

\todo{import from paper}

@@

@@

%%  LocalWords:  summarisation
